Recruiting Chapter

### 2021-05-18 text/tables_figures_may_2021.Rmd
draft changes

  if (type == 'Region') {
    ordered_df <- df %>% arrange(univ_region, univ_name)
  } else {
    ordered_df <- df %>% arrange(rank, univ_name)
  }

@@

```

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE, include = FALSE}
#all univ privu all_pubu_outst pub pubu_outst
# running one plot at a time

# region

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'region', '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 1))

  a <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
  )

  b <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
  )

  c <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privc', '.RDS'))),
    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
  )

  grid.arrange(a, b, c, nrow=3, ncol=1)

@@

# religion

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'religion', '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 1))

  a <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'), visit_count = TRUE
  )

  b <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
    'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'), visit_count = TRUE
  )

  grid.arrange(a, b, nrow=2, ncol=1)

# racial composition

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'race', '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 1))

  a <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE
  )

  b <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
    '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE
  )

  grid.arrange(a, b, nrow=2, ncol=1)

# academic reputation

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'hs_rank', '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 1))

  a <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'), visit_count = TRUE
  )

  b <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
    'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'), visit_count = TRUE
  )

  grid.arrange(a, b, nrow=2, ncol=1)

```

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE, eval = FALSE}

type_vec <- c('pubu', 'pubu_outst','privu','univ','univ_pubu_outst')
#type_vec <- c('privu', 'pubu', 'pubu_outst', 'all', 'all_pubu_outst')

for (i in 1:length(type_vec)) {
  ego_df <-readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 2))

  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE)
  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE)
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))

  grid.arrange(a, b, c, d, nrow=2, ncol=2, widths=c(1, 0.92))
  dev.off()

  # Need to use print() for ggplot inside loop in order for it to appear
  # https://stackoverflow.com/a/15678596/6373540
  # print(a)
  # print(b)
  # print(c)
  # print(d)
}
```

@@

```{r ego-network-figure-region, fig.align = 'center', echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_region.pdf')
```

@@

```{r ego-network-figure-religion, fig.align = 'center', echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_religion.pdf')
```

@@

```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "Academic reputation of of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank.pdf')
```

@@

```{r ego-network-figure-race, fig.align = 'center', echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
knitr::include_graphics('./../assets/figures/ego_network_figure_race.pdf')
```

```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, eval=FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
knitr::include_graphics('./../assets/figures/ego_network_figure_privu.pdf')
```

@@

```{r privhs-universe, fig.align = 'center', echo = FALSE, eval = FALSE,fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
knitr::include_graphics('./../assets/figures/plot_pss_universe.pdf')
```

<!-- 
\begin{center}
* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12 students and is not a special education school, an alternative school, an early childhood center, or an independent school.}
\end{center}
-->

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
knitr::include_graphics('./../assets/figures/plot_2mode_all_region.pdf')

@@

```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for private institutions, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
```

@@

```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}
knitr::include_graphics('./../assets/figures/villanova_religion.pdf')
```

```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, colored by geographic region"}
knitr::include_graphics('./../assets/figures/emory_region.pdf')
```

```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
```

```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions and out-of-state visits only, colored by cluster", eval = FALSE}
knitr::include_graphics('./../assets/figures/plot_1mode_pubu_outst.pdf')
```

```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by public institutions"}
knitr::include_graphics('./../assets/figures/ego_network_figure_pubu.pdf')
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}

```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, colored by cluster", include= FALSE, eval = FALSE}
knitr::include_graphics('./../assets/figures/plot_1mode_all.pdf')
```

```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_all_pubu_outst.pdf')
```

```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by all institutions, out-of-state visits only for public universities"}
knitr::include_graphics('./../assets/figures/ego_network_figure_all_pubu_outst.pdf')
#out.width="1.1\\linewidth", 
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}

>>>>

  if (type == 'region') {
    ordered_df <- df %>% arrange(univ_region, univ_name)
  } else {
    ordered_df <- df %>% arrange(rank, univ_name)
  }

@@

# create function to run the plot_characteristic() function
#plot_characteristic <- function(df, type, characteristic, label_text, visit_count = FALSE) {

run_plot_characteristics <- function(which_psi,which_char,char_label,which_vars,which_labels) {

  # stuff to use later
    num_plot <- length(which_psi)
    name_suf <- str_c(which_psi,collapse = '_')

  #print function values as a check
    print(which_psi)
    #print(name_suf)
    #print(num_plot)
    print(str_c('which_char=',which_char))
    print(str_c('char_label=',char_label))
    #print(which_vars)
    #print(which_labels)

  # initiate pdf
  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', which_char,'_',name_suf, '.pdf')))
    par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
    par(mfrow=c(2, 1))

  #loop to create figure separately for each psi type
  plot_list <- vector("list", length(which_psi))
  for (i in 1:length(which_psi)) {

    plot_list[[i]] <- plot_characteristic(
      df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', which_psi[i], '.RDS'))),
      #df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
      type = char_label,
      characteristic = which_vars,
      label_text = which_labels,
      visit_count = TRUE
    )

  }

  # plot sub-plots in grid
  do.call("grid.arrange", c(plot_list, nrow=num_plot, ncol=1))

@@

}

# region
  # pubu, privu, privc
  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'region', char_label = 'Region', which_vars = c('northeast', 'midwest', 'south', 'west'),which_labels =c('Northeast', 'Midwest', 'South', 'West'))
  # pubu and privu
  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'region', char_label = 'Region', which_vars = c('northeast', 'midwest', 'south', 'west'),which_labels =c('Northeast', 'Midwest', 'South', 'West'))

# religion
  # pubu, privu, privc
  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'religion', char_label = 'Religion', which_vars = c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))

  # pubu, privu
  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'religion', char_label = 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))

# high school rank
  # pubu, privu, privc
  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'hs_rank', char_label = 'HS rank', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))
  # pubu, privu  
  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'hs_rank', char_label = 'HS rank', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))

# racial composition
  # pubu, privu, privc  
  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'pct_black_latinx_native', char_label = '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'))  
  # pubu, privu  
  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'pct_black_latinx_native', char_label = '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'))

  plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE
  )
```

@@

```{r privhs-universe, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private high schools"}
knitr::include_graphics('./../assets/figures/plot_pss_universe.pdf')
```

\begin{center}
* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12.}
\end{center}

@@

```{r ego-network-figure-region, fig.align = 'center', echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
#knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu_privc.pdf')
knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu.pdf')
```

@@

```{r ego-network-figure-religion, fig.align = 'center', echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
#knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu_privc.pdf')
knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu.pdf')
```

@@

```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "High school rank of visited private high schools"}
#knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu_privc.pdf')
knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu.pdf')
```

@@

```{r ego-network-figure-race, fig.align = 'center', echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
#knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu_privc.pdf')
knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu.pdf')
```

@@

```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
```

```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
```

```{r plot-1mode-privc, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private liberal arts colleges, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_privc.pdf')
```

```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
```

```{r plot-1mode-u-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster, five clusters"}
knitr::include_graphics('./../assets/figures/plot_1mode_u_k5.pdf')
```

```{r plot-1mode-all, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_all.pdf')
```

```{r plot-1mode-all-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster, five clusters"}
knitr::include_graphics('./../assets/figures/plot_1mode_all_k5.pdf')
```

```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, out-of-state visits only, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_pubu_outst.pdf')
```

```{r plot-1mode-u-pubu-outst, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, out-of-state visits only for public universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_u_pubu_outst.pdf')
```

```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "One-mode network for all institutions, out-of-state visits only for public universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_all_pubu_outst.pdf')
```

```{r two-mode-plot, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
# <!-- plot of two-mode network; exclude for now -->
knitr::include_graphics('./../assets/figures/plot_2mode_all_region.pdf')

@@

```{r villanova-religion, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}
#<!-- Ego networks; exclude for now -->
knitr::include_graphics('./../assets/figures/villanova_religion.pdf')
```

```{r emory-region, fig.align = 'center', echo = FALSE, eval= FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, colored by geographic region"}
knitr::include_graphics('./../assets/figures/emory_region.pdf')
```

@@
